---
title: "COVID-19 Meta-Analysis of Comorbidities"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source_code: embed
    theme: yeti
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(metafor)
#library(metaviz)
library(googlesheets4)
library(htmltools)
  sheets_deauth()
  
  dat <- read_sheet("1m4cxVwr1D0MUWL2w_0UvdA19tSd1m5KYKKXnveZW-io")

  measureType <- "PR"
  
  dat_fever <- escalc(
    measure = measureType,
    xi = symptomsFeverProp,
    ni = Patients_Total,
    data = dat
  )
  
  dat_cough <- escalc(
    measure = measureType,
    xi = symptomsCoughProp,
    ni = Patients_Total,
    data = dat
  )

  dat_fatigue <- escalc(
    measure = measureType,
    xi = symptomsFatigueProp,
    ni = Patients_Total,
    data = dat
  )    

  dat_dyspnea <- escalc(
    measure = measureType,
    xi = symptomsDyspneaProp,
    ni = Patients_Total,
    data = dat
  )

  dat_hypertension <- escalc(
    measure = measureType,
    xi = symptomsHypertensionProp,
    ni = Patients_Total,
    data = dat
  )
  
  dat_diabetes <- escalc(
    measure = measureType,
    xi = symptomsDiabetesProp,
    ni = Patients_Total,
    data = dat
  )
  
  dat_rsd <- escalc(
    measure = measureType,
    xi = symptomsRespiratorySystemDiseaseProp,
    ni = Patients_Total,
    data = dat
  )

  dat_csd <- escalc(
    measure = measureType,
    xi = symptomsCardiovascularDiseaseProp,
    ni = Patients_Total,
    data = dat
  )
  
  res.fever <- rma(yi,vi,slab = Study, data = dat_fever)
  res.cough <- rma(yi,vi,slab = Study, data = dat_cough)
  res.fatigue<- rma(yi,vi,slab = Study, data = dat_fatigue)
  res.dyspnea <- rma(yi,vi,slab = Study, data = dat_dyspnea)
  res.hypertension <- rma(yi,vi,slab = Study, data = dat_hypertension)
  res.diabetes <- rma(yi,vi,slab = Study, data = dat_diabetes)
  res.rsd <- rma(yi,vi,slab = Study, data = dat_rsd)
  res.csd <- rma(yi,vi,slab = Study, data = dat_csd)
  
  #includeHTML("google-analytics.html")
```



Fever
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Forest Plot

```{r}
forest(res.fever)
```

### Funnel Plot

```{r fig.height=5, fig.width=7}
#funnel(res.fever)
funnel(res.fever, level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), legend=TRUE)
```

Column {data-width=500}
-----------------------------------------------------------------------

### Model Output

```{r}
res.fever
```

### Publication Bias

```{r}
ranktest(res.fever)

regtest(res.fever)

#includeHTML("google-analytics.html")
```


Cough
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Forest Plot

```{r}
forest(res.cough)
```

### Funnel Plot

```{r fig.height=5, fig.width=7}
#funnel(res.fever)
funnel(res.cough, level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), legend=TRUE)
```

Column {data-width=500}
-----------------------------------------------------------------------

### Model Output

```{r}
res.cough
```

### Publication Bias

```{r}
ranktest(res.cough)

regtest(res.cough)

```

Fatigue
=======================================================================
  
  Column {data-width=500}
-----------------------------------------------------------------------
  
### Forest Plot
  
```{r}
forest(res.fatigue)
```

### Funnel Plot

```{r fig.height=5, fig.width=7}
#funnel(res.fever)
funnel(res.fatigue, level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), legend=TRUE)
```

Column {data-width=500}
-----------------------------------------------------------------------
  
### Model Output
  
  ```{r}
res.fatigue
```

### Publication Bias

```{r}
ranktest(res.fatigue)

regtest(res.fatigue)

```

Dyspnea
=======================================================================
  
  Column {data-width=500}
-----------------------------------------------------------------------
  
### Forest Plot
  
```{r}
forest(res.dyspnea)
```

### Funnel Plot

```{r fig.height=5, fig.width=7}
#funnel(res.fever)
funnel(res.dyspnea, level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), legend=TRUE)
```

Column {data-width=500}
-----------------------------------------------------------------------
  
### Model Output
  
```{r}
res.dyspnea
```

### Publication Bias

```{r}
ranktest(res.dyspnea)

regtest(res.dyspnea)

```

Hypertension
=======================================================================
  
  Column {data-width=500}
-----------------------------------------------------------------------
  
### Forest Plot
  
```{r}
forest(res.hypertension)
```

### Funnel Plot

```{r fig.height=5, fig.width=7}
#funnel(res.fever)
funnel(res.hypertension, level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), legend=TRUE)
```

Column {data-width=500}
-----------------------------------------------------------------------
  
### Model Output
  
```{r}
res.hypertension
```

### Publication Bias

```{r}
ranktest(res.hypertension)

regtest(res.hypertension)

```

Diabetes
=======================================================================
  
  Column {data-width=500}
-----------------------------------------------------------------------
  
### Forest Plot
  
```{r}
forest(res.diabetes)
```

### Funnel Plot

```{r fig.height=5, fig.width=7}
#funnel(res.fever)
funnel(res.diabetes, level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), legend=TRUE)
```

Column {data-width=500}
-----------------------------------------------------------------------
  
### Model Output

```{r}
res.diabetes
```

### Publication Bias

```{r}
ranktest(res.diabetes)

regtest(res.diabetes)

```

Respiratory Disease
=======================================================================
  
  Column {data-width=500}
-----------------------------------------------------------------------
  
### Forest Plot
  
```{r}
forest(res.rsd)
```

### Funnel Plot

```{r fig.height=5, fig.width=7}
#funnel(res.fever)
funnel(res.rsd, level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), legend=TRUE)
```

Column {data-width=500}
-----------------------------------------------------------------------
  
### Model Output
  
```{r}
res.rsd
```

### Publication Bias

```{r}
ranktest(res.rsd)

regtest(res.rsd)

```

Cardiovascular Disease
=======================================================================
  
  Column {data-width=500}
-----------------------------------------------------------------------
  
### Forest Plot
  
```{r}
forest(res.csd)
```

### Funnel Plot

```{r fig.height=5, fig.width=7}
#funnel(res.fever)
funnel(res.csd, level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), legend=TRUE)
```

Column {data-width=500}
-----------------------------------------------------------------------
  
### Model Output
  
```{r}
res.csd
```

### Publication Bias

```{r}
ranktest(res.csd)

regtest(res.csd)

```

About
=======================================================================
This is a living meta-analysis based off the work of Jing Yang and collequges. 

Yang, J., Zheng, Y., Gou, X., Pu, K., Chen, Z., Guo, Q., Ji, R., Wang, H., Wang, Y., & Zhou, Y. (2020). Prevalence of comorbidities in the novel Wuhan coronavirus (COVID-19) infection: a systematic review and meta-analysis. International Journal of Infectious Diseases. https://doi.org/10.1016/j.ijid.2020.03.017